The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-17 analysis/paper/paper.qmd
Remove stop words from text_clean column

meta_stopwords <- find_meta_stopwords(emu_theses, convert_to_regex = FALSE)
urbanism_stopwords <- urbanism_stopwords() 
thesis_stopwords <- thesis_stopwords()

emu_theses_words <- emu_theses |> 
  select(title, text) |>  
  unnest_tokens(output = word, input = text) |>   # remove punctuation, convert to lowercase, seperate all words
  anti_join(stop_words, by = "word") |> 
  anti_join(urbanism_stopwords, by = "word") |> 
  anti_join(thesis_stopwords, by = "word")
```

>>>>

urbanism_stopwords <- urbanism_stopwords() 
thesis_stopwords <- thesis_stopwords()

emu_theses_words <- emu_theses |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>   # remove punctuation, convert to lowercase, seperate all words
  anti_join(stop_words, by = "word") |> 
  anti_join(urbanism_stopwords, by = "word") |> 
  anti_join(thesis_stopwords, by = "word")
```
